Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-03-23 summary.Rmd
typos

\begin{proof}
Define the following matrices from $\{\lambda^{(kl)}\}_K$: 
$$\Lambda^{(k)} = 
\begin{bmatrix} \lambda^{(k,1)} & \cdots & \lambda^{(k, K)} \end{bmatrix}
\in \mathbb{R}^{n_k \times K}$$

@@

**Proof of Theorem \ref{theorem3}**.
By Lemma 3.1, $V V^\top = X (X^\top X)^{-1} X^\top$ where $X$ is defined as 
in Theorem 2. Since $X$ is block diagonal with each block corresponding 
to one community, $X (X^\top X)^{-1} X^\top$ is also a block diagonal matrix 
with each block corresponding to a community and zeros elsewhere. Therefore, 
if vertices $i$ and $j$ belong to different communities, then the $ij$^th^ 
element of $X (X^\top X)^{-1} X^\top = V V^\top = B$ is 0.

>>>>

\begin{proof}
Define the following matrices from $\{\lambda^{(kl)}\}_K$:

$$\Lambda^{(k)} = 
\begin{bmatrix} \lambda^{(k,1)} & \cdots & \lambda^{(k, K)} \end{bmatrix}
\in \mathbb{R}^{n_k \times K}$$

@@

**Proof of Theorem \ref{theorem3}**.
By Lemma \ref{lemma1}, $V V^\top = X (X^\top X)^{-1} X^\top$ where $X$ is 
defined as in (\ref{eq:xy}). Since $X$ is block diagonal with each 
block corresponding to one community, $X (X^\top X)^{-1} X^\top$ is also a 
block diagonal matrix with each block corresponding to a community and zeros
elsewhere. Therefore, if vertices $i$ and $j$ belong to different communities,
then the $ij$^th^ element of $n X (X^\top X)^{-1} X^\top = n V V^\top = B$ 
is 0.
